---
title: "Untitled"
author: "RN7"
date: "1/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# pkgs

```{r, message=FALSE, warning=FALSE}
pacman::p_load(tidyverse, polite, scales, ggimage, 
               ggforce, ggtext,
               rvest, glue, extrafont, ggrepel, magick)
loadfonts()
```

## add_logo

```{r}
add_logo <- function(plot_path, logo_path, logo_position, logo_scale = 10){

    # Requires magick R Package https://github.com/ropensci/magick

    # Useful error message for logo position
    if (!logo_position %in% c("top right", "top left", "bottom right", "bottom left")) {
        stop("Error Message: Uh oh! Logo Position not recognized\n  Try: logo_positon = 'top left', 'top right', 'bottom left', or 'bottom right'")
    }

    # read in raw images
    plot <- magick::image_read(plot_path)
    logo_raw <- magick::image_read(logo_path)

    # get dimensions of plot for scaling
    plot_height <- magick::image_info(plot)$height
    plot_width <- magick::image_info(plot)$width

    # default scale to 1/10th width of plot
    # Can change with logo_scale
    logo <- magick::image_scale(logo_raw, as.character(plot_width/logo_scale))

    # Get width of logo
    logo_width <- magick::image_info(logo)$width
    logo_height <- magick::image_info(logo)$height

    # Set position of logo
    # Position starts at 0,0 at top left
    # Using 0.01 for 1% - aesthetic padding

    if (logo_position == "top right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "top left") {
        x_pos = 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "bottom right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    } else if (logo_position == "bottom left") {
        x_pos = 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    }

    # Compose the actual overlay
    magick::image_composite(plot, logo, offset = paste0("+", x_pos, "+", y_pos))
}
```

# Bundesliga data

## fbref

- Save "Player Standard Stats" & "Squad Standard Stats" as a `.csv` file or whatever you prefer.
- https://fbref.com/en/comps/20/stats/Bundesliga-Stats

### squad stats

```{r}
buli_squad_stats_hinrunde_raw <- read_csv(here::here("data/buli_squad_stats_hinrunde.csv"),
                                 skip = 1, col_names = TRUE)

buli_squad_stats_hinrunde <- buli_squad_stats_hinrunde_raw %>% 
  rename_at(vars(12:16), 
            ~ glue::glue("{colnames(buli_squad_stats_hinrunde_raw)[12:16]}_p90")) %>% 
  rename_at(vars(20:24), 
            ~ glue::glue("{colnames(buli_squad_stats_hinrunde_raw)[20:24]}_p90"))

buli_squad_stats_hinrunde <- buli_squad_stats_hinrunde %>% 
  rename_at(vars(2:24), ~ glue::glue("{colnames(buli_squad_stats_hinrunde)[2:24]}_squad")) %>% 
  rename_at(vars(contains("_1")), ~ str_replace(., "_1", ""))

glimpse(buli_squad_stats_hinrunde)
```

```{r}
## save
saveRDS(buli_squad_stats_hinrunde, file = glue("{here::here()}/data/buli_squad_stats_hinrunde.RDS"))
buli_squad_stats_hinrunde <- readRDS(file = glue("{here::here()}/data/buli_squad_stats_hinrunde.RDS"))
```

### player stats

```{r}
buli_player_stats_hinrunde_raw <- read_csv(here::here("data/buli_player_stats_hinrunde.csv"),
                                  skip = 1, col_names = TRUE)

buli_player_stats_hinrunde <- buli_player_stats_hinrunde_raw %>% 
  rename_at(vars(17:21), 
            ~ glue::glue("{colnames(buli_player_stats_hinrunde_raw)[17:21]}_p90")) %>% 
  rename_at(vars(25:29), 
            ~ glue::glue("{colnames(buli_player_stats_hinrunde_raw)[25:29]}_p90"))

buli_player_stats_hinrunde <- buli_player_stats_hinrunde %>% 
  rename_at(vars(contains("_1")), ~ str_replace(., "_1", "")) %>% 
  select(-Matches, -Rk)
  

glimpse(buli_player_stats_hinrunde)
```

```{r}
## save
saveRDS(buli_player_stats_hinrunde, file = glue("{here::here()}/data/buli_player_stats_hinrunde.RDS"))
buli_player_stats_hinrunde <- readRDS(file = glue("{here::here()}/data/buli_player_stats_hinrunde.RDS"))
```


## clean

```{r}
goal_contribution_clean_df <- buli_player_stats_hinrunde %>% 
  left_join(buli_squad_stats_hinrunde, by = "Squad") %>% 
  separate(Player, into = c("fullname", "allname"), sep = "\\\\") %>% 
  separate(fullname, into = c("firstname", "lastname"),
           sep = "\\s", extra = "merge",
           remove = FALSE) %>%
  mutate(fname = str_extract(firstname, "[A-Z]{1}")) %>% 
  ## players like Fabinho listed without Tavares last name
  mutate(player = if_else(is.na(lastname), firstname, lastname)) %>% 
  mutate(player = case_when(
    !is.na(lastname) ~ glue("{fname}. {lastname}"),
    TRUE ~ firstname)) %>% 
  group_by(fullname) %>% 
  mutate(goal_contrib = Gls / Gls_squad,
         assist_contrib = Ast / Gls_squad) %>% 
  ungroup() %>% 
  ## keep fullname so can differentiate A. Gomes (Andre/Angel), etc.
  select(player, fullname, Pos, Squad, Min,
         Gls, Gls_squad, PK, PK_squad, 
         Ast, Ast_squad,
         goal_contrib, assist_contrib,
         npxG_p90, xA_p90, npxG, xA) 

glimpse(goal_contribution_clean_df)
```



## plot

```{r}
goal_contribution_clean_df %>% 
  filter(Min >= 900,
         Pos %in% c("FW", "FWMF")) %>% 
  summarize(avg_goal_contrib = median(goal_contrib),
            avg_assist_contrib = median(assist_contrib))
```


### goals & assists


```{r fig.width = 14, fig.height = 10}  
## Description text
desc_andersson <- "Union Berlin had a rought start to their maiden Bundesliga season but Andersson stepped up to scoring vitals goals in wins against fellow relegation candidates like Mainz and FC Köln"

desc_weghorst <- "With "

desc_nieder <- "Niederlechner is on course to beat his best Bundesliga season (11 Goals | 3 Assists with Freiburg in 16/17) by quite a margin with 8 goals and 6 assists so far. His total contribution (goals and assists) equals to half of Augburg's goals in the hinrunde."

desc_volland <- "Volland is the fulcrum of Leverkusen's bid for a consecutive appearance in the Champions League with 5 goals and 6 assists. He tallied up 0.45 xG per 90 (11th in the league) and 0.28 xA per 90 (10th) in the Hinrunde."

## PLOT!
goal_contribution_matrix <- goal_contribution_clean_df %>% 
  ggplot(aes(assist_contrib, goal_contrib)) +
  geom_point(data = goal_contribution_clean_df %>%
               filter(goal_contrib < 0.2 | assist_contrib < 0.15),
             color = "grey20", size = 4, alpha = 0.2) +
  geom_point(data = goal_contribution_clean_df %>%
               filter(goal_contrib > 0.2 | assist_contrib > 0.15),
             color = "red", size = 4) +
  geom_hline(yintercept = 0.157, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 0.08, color = "grey20", alpha = 0.4) +
  geom_text_repel(
    data = goal_contribution_clean_df %>%
      filter(goal_contrib > 0.2 | assist_contrib > 0.15, 
             !player %in% c("S. Andersson", "W. Weghorst", 
                            "F. Niederlechner", "K. Volland")),
    aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
    seed = 15, size = 4, 
    min.segment.length = 0, segment.color = "red",
    point.padding = 0.5) +
  geom_mark_circle(
    aes(filter = player == "S. Andersson", 
        label = "Sebastian Andersson",
        description = desc_andersson), 
    label.width = unit(65, 'mm'), label.buffer = unit(5, "mm"),
    label.family = "Roboto Condensed", label.fontsize = c(14, 12)) +
  geom_mark_hull(
    aes(filter = player == "W. Weghorst", 
        label = "Wout Weghorst",
        description = desc_weghorst),
    label.width = unit(45, 'mm'), label.buffer = unit(5, "mm"), label.fontsize = c(14, 11),
    label.family = "Roboto Condensed") +
  geom_mark_hull(
    aes(filter = player == "F. Niederlechner", 
        label = "Florian Niederlechner",
        description = desc_nieder), 
    concavity = 1,
    label.width = unit(55, 'mm'), label.buffer = unit(0.1, "mm"),
    label.fontsize = c(14, 12), label.family = "Roboto Condensed") +
  geom_mark_hull(
    aes(filter = player == "K. Volland", 
        label = "Kevin Volland",
        description = desc_volland), 
    concavity = 1,
    label.width = unit(65, 'mm'), label.buffer = unit(40.5, "mm"),
    label.fontsize = c(14, 12), label.family = "Roboto Condensed") +
  scale_x_continuous(labels = percent_format(accuracy = 1), 
                     breaks = c(0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3),
                     limits = c(0, 0.35)) +
  scale_y_continuous(labels = percent_format(accuracy = 1), 
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(0, 0.57)) +
  labs(title = "Goal Involvement: <b style='color: red'>Bundesliga</b> (2019-2020 Season)", 
       subtitle = glue("
                       Goal Involvement (Goals or Assists) as Percentage of Total Club Goals
                       Hinrunde | January 13th, 2020"),
       caption = glue("
                      Data: FBref | StatsBomb
                      Ryo Nakagawara, Twitter: @R_by_Ryo"),
       x = "Percentage of Club Goals Assisted",
       y = "Percentage of Club Goals Scored") +
  theme_minimal() +
  theme(text = element_markdown(family = "Roboto Condensed"),
        plot.title = element_markdown(size = 20),
        plot.subtitle = element_text(size = 16),
        plot.caption = element_text(size = 14),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        panel.grid.minor.x = element_blank())

goal_contribution_matrix
```



```{r fig.width = 14, fig.height = 10}  
## Description text
desc_labels <- c(
"Union Berlin had a rought start to their maiden Bundesliga season but Andersson stepped up to scoring vitals goals in wins against fellow relegation candidates like Mainz and FC Köln",

"With ",

"Niederlechner is on course to beat his best Bundesliga season (11 Goals | 3 Assists with Freiburg in 16/17) by quite a margin with 8 goals and 6 assists so far. His total contribution (goals and assists) equals to half of Augburg's goals in the hinrunde.",

"Volland is the fulcrum of Leverkusen's bid for a consecutive appearance in the Champions League with 5 goals and 6 assists. He tallied up 0.45 xG per 90 (11th in the league) and 0.28 xA per 90 (10th) in the Hinrunde.")

## PLOT!
goal_contribution_matrix <- goal_contribution_clean_df %>% 
  ggplot(aes(assist_contrib, goal_contrib)) +
  geom_point(data = goal_contribution_clean_df %>%
               filter(goal_contrib < 0.2 | assist_contrib < 0.15),
             color = "grey20", size = 4, alpha = 0.2) +
  geom_point(data = goal_contribution_clean_df %>%
               filter(goal_contrib > 0.2 | assist_contrib > 0.15),
             color = "red", size = 4) +
  geom_hline(yintercept = 0.157, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 0.08, color = "grey20", alpha = 0.4) +
  geom_text_repel(
    data = goal_contribution_clean_df %>%
      filter(goal_contrib > 0.2 | assist_contrib > 0.15, 
             !player %in% c("S. Andersson", "W. Weghorst", 
                            "F. Niederlechner", "K. Volland")),
    aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
    seed = 15, size = 4, 
    min.segment.length = 0, segment.color = "red",
    point.padding = 0.5) +
  geom_mark_circle(
    aes(filter = player %in% c("S. Andersson", "W. Weghorst", 
                            "F. Niederlechner", "K. Volland"), 
        description = desc_labels), 
    label.width = unit(65, 'mm'), label.buffer = unit(5, "mm"),
    label.family = "Roboto Condensed", label.fontsize = c(14, 12)) +
  scale_x_continuous(labels = percent_format(accuracy = 1), 
                     breaks = c(0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3),
                     limits = c(0, 0.35)) +
  scale_y_continuous(labels = percent_format(accuracy = 1), 
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(0, 0.57)) +
  labs(title = "Goal Involvement: <b style='color: red'>Bundesliga</b> (2019-2020 Season)", 
       subtitle = glue("
                       Goal Involvement (Goals or Assists) as Percentage of Total Club Goals
                       Hinrunde | January 13th, 2020"),
       caption = glue("
                      Data: FBref | StatsBomb
                      Ryo Nakagawara, Twitter: @R_by_Ryo"),
       x = "Percentage of Club Goals Assisted",
       y = "Percentage of Club Goals Scored") +
  theme_minimal() +
  theme(text = element_markdown(family = "Roboto Condensed"),
        plot.title = element_markdown(size = 20),
        plot.subtitle = element_text(size = 16),
        plot.caption = element_text(size = 14),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        panel.grid.minor.x = element_blank())

goal_contribution_matrix
```








#### save

```{r}
ggsave(plot = goal_contribution_matrix, 
       here::here("Premier League 2019-2020/output/goal_contribution_plot_1920_MD20.png"),
       height = 9, width = 11)
```

```{r}
plot_logo <- add_logo(
  plot_path = here::here("Premier League 2019-2020/output/goal_contribution_plot_1920_MD20.png"),
  logo_path = "https://upload.wikimedia.org/wikipedia/en/f/f2/Premier_League_Logo.svg",
  logo_position = "top right",
  logo_scale = 6)

plot_logo
```

```{r}
image_write(image = plot_logo, 
            here::here("Premier League 2019-2020/output/goal_contribution_plot_1920_MD20_logo.png"))
```




### xG 


```{r}
goal_contribution_clean_df %>% 
  filter(Min >= 900,
         Pos %in% c("FW", "FWMF")) %>% 
  summarize(avg_npxg90 = median(npxG_p90),
            avg_xA = median(xA_p90))

goal_contribution_clean_df %>% 
  filter(Min >= 900,
         Pos %in% c("FW")) %>% 
  summarize(avg_npxg90 = median(npxG_p90),
            avg_xA = median(xA_p90))
```


```{r}
xG_xA_per90 <- goal_contribution_clean_df
```

```{r}
xG_xA_per90 %>% 
  filter(Min >= 900,
         Pos %in% c("FW", "FWMF")) %>% 
  summarize(avg_npxg90 = median(npxG_p90),
            avg_xA = median(xA_p90))
```

- Buendia: 3.35 KP per 90 (3rd)
- G. Jesus (4.55 sh/90, 1., 1.88 SOT/90, 2. just behind Mahrez 1.89)
- Aguero (0.66 np-xG per 90, 2., 6.6 np-xG, 8 np-Goals) + Sterling (0.47 np-xG per 90, 7., 0.26 xA per 90, 7.)
- Mahrez (3.33 PPA per 90, 2nd. 2.77 KP per 90, 7th) + De Bruyne (3.56 PPA per 90. 4.02 KP per 90, 1st)
- lots of attacking fullbacks in bottom: Trent, Robbo, Chilwell, Azpi, Max Aarons, Digne, Matt Targett

```{r}
desc_jesus <- "Despite a rocky start to the season and the eventual firing of Niko Kovac, Bayern maintained great attacking output mainly through Robert Lewandowski's unreal finishing! Thomas Müller, who had been frozen out by Kovac, got back to form under new manager Hansi Flick."

desc_aguero_sterling <- "With only 1 goal in the last 6 league games City is in desperate need for Aguero to get firing again as his 8 np-Goals from 6.6 np-xG is more clinical than Gabriel Jesus. Raheem Sterling is City's top scorer with 11 goals from 8.7 np-xG and is in the top 10 for xG and xA per 90 showing his dual threat."

desc_mahrez_debruyne <- "Mahrez & De Bruyne create the chances that Sterling, Aguero, and to a lesser extent - Gabriel Jesus convert. The two lead the league in Passes into the Penalty Area (PPA) while De Bruyne racks up 3.86 Key Passes (KP) per 90, the best in the league by far."
```


```{r fig.width = 12, fig.height = 10}
xG_xA_per90_plot <- xG_xA_per90 %>% 
  filter(Min >= 900) %>% 
  ggplot(aes(xA_p90, npxG_p90)) +
  geom_point(data = xG_xA_per90 %>%
               filter(xA_p90 < 0.15 | npxG_p90 < 0.3,
                      Min >= 900),
             color = "grey20", size = 4, alpha = 0.2) +
  geom_point(data = xG_xA_per90 %>%
               filter(xA_p90 > 0.15 | npxG_p90 > 0.3,
                      Min >= 900),
             color = "red", size = 4) +
  geom_hline(yintercept = 0.3, color = "red", alpha = 0.6) +
  geom_vline(xintercept = 0.15, color = "red", alpha = 0.6) +
  ## All player labels
  geom_text_repel(
    data = xG_xA_per90 %>%
      filter(xA_p90 > 0.15 | npxG_p90 > 0.3,
             !player %in% c("R. Lewandowski", 
                            "S. Gnabry", "T. Müller",
                            "M. Thuram", 
                            "B. Embolo", "A. Pléa",
                            "K. Volland", 
                            "F. Niederlechner",
                            "T. Werner"),
             Min >= 900),
    aes(label = player, family = "Roboto Condensed", 
        fontface = "bold"),
    seed = 15, size = 3.5,
    min.segment.length = 0, segment.color = "red",
    point.padding = 0.5) +
  ## Bayern player labels
  geom_text_repel(
    data = xG_xA_per90 %>%
      filter(player %in% c("R. Lewandowski", 
                            "S. Gnabry", "T. Müller")),
    aes(label = player, family = "Roboto Condensed", 
        fontface = "bold"),
    seed = 15, size = 4.5, color = "red",
    min.segment.length = 0, segment.color = "red",
    point.padding = 0.5, nudge_y = 0.05) +
  ## Gladbach player labels
  geom_text_repel(
    data = xG_xA_per90 %>%
      filter(player %in% c("M. Thuram", 
                           "B. Embolo", "A. Pléa")),
    aes(label = player, family = "Roboto Condensed", 
        fontface = "bold"),
    seed = 15, size = 4.5, color = "#228B22",
    min.segment.length = 0, segment.color = NA,
    point.padding = 0.3) +
  # geom_text(
  #   data = xG_xA_per90 %>%
  #     filter(player == "R. Sterling"),
  #   aes(label = player, family = "Roboto Condensed", 
  #       fontface = "bold"),
  #   size = 4.5, nudge_x = 0.03, nudge_y = 0.025,
  #   color = "#6CABDD") +
  # geom_text_repel(
  #   data = xG_xA_per90 %>%
  #     filter(player %in% c("S. Agüero",
  #                          "R. Mahrez", "K. De Bruyne")),
  #   aes(label = player, family = "Roboto Condensed", 
  #       fontface = "bold"),
  #   seed = 15, size = 4.5, color = "#6CABDD",
  #   min.segment.length = 0, segment.color = "red",
  #   point.padding = unit(3, "mm")) +
  ## Bayern description
  geom_mark_hull(
    aes(filter = player %in% c("R. Lewandowski", 
                               "S. Gnabry", 
                               "T. Müller"),
        label = "Bayern's Attack Remains Strong.",
        description = desc_jesus),
    expand = unit(2.5, "mm"),
    label.width = unit(90, 'mm'), label.buffer = unit(5, "mm"),
    label.family = "Roboto Condensed", label.fontsize = c(14, 12),
    label.colour = c("red", "black")) +
  ## Gladbach description
  geom_mark_hull(
    aes(filter = player %in% c("M. Thuram", 
                               "B. Embolo"), 
        label = "Gladbach's Attacking Trio",
        description = desc_aguero_sterling),
    expand = unit(0.05, "mm"), label.width = unit(60, 'mm'),
    label.buffer = unit(30, "mm"), label.fontsize = c(14, 11),
    label.family = "Roboto Condensed", 
    label.colour = c("#228B22", "black")) +
  geom_mark_circle(
    aes(filter = player == "A. Pléa"),
    expand = unit(3, "mm"), label.width = unit(50, 'mm'),
    label.buffer = unit(30, "mm"), label.fontsize = c(14, 11),
    label.family = "Roboto Condensed", 
    label.colour = c("#228B22", "black")) +
  ## Gladbach desc.
  annotate("text", family = "Roboto Condensed", 
           fontface = "bold",
           x = 0.37, y = 0.4, 
           label = "blargh blargh") +
  ## xG and xA league average
  annotate("text", family = "Roboto Condensed", fontface = "bold",
           x = 0.15, y = 0.935, hjust = 0, color = "red",
           label = "Average xA per 90: 0.15") +
  annotate("text", family = "Roboto Condensed", fontface = "bold",
           x = 0.59, y = 0.29, color = "red",
           label = "Average np-xG per 90: 0.3") +
  scale_x_continuous(labels = seq(0, 0.9, 0.1), 
                     breaks = seq(0, 0.9, 0.1),
                     limits = c(0, 0.65)) +
  scale_y_continuous(labels = seq(0, 0.9, 0.1), 
                     breaks = seq(0, 0.9, 0.1),
                     limits = c(0, 0.95)) +
  labs(title = "<b style='color: #6CABDD'>City's Attackers </b> Dominate the 'Expected' Stats: xG per 90 & xA per 90", 
       subtitle = glue("
                       Bundesliga (2019-2020 Season) | Hinrunde | January 13th, 2020
                       <p><b style='color: red'>Average (Median)</b> for Midfielders/Forwards | Minimum 900 Minutes Played"),
       caption = glue("
                      Data: FBref | StatsBomb
                      Ryo Nakagawara, Twitter: @R_by_Ryo"),
       x = "Expected Assists (xA) per 90",
       y = "non-Penalty Expected Goals (np-xG) per 90") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        plot.title = element_markdown(size = 18),
        plot.subtitle = element_markdown(size = 16),
        plot.caption = element_text(size = 14),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        panel.grid.minor.x = element_blank())

xG_xA_per90_plot
```



```{r fig.width = 12, fig.height = 10}
xG_xA_per90 %>% 
  filter(Min >= 900) %>% 
  ggplot(aes(xA_p90, npxG_p90)) +
  geom_point(data = xG_xA_per90 %>%
               filter(xA_p90 < 0.15 | npxG_p90 < 0.3,
                      Min >= 900),
             color = "grey20", size = 4, alpha = 0.2) +
  geom_point(data = xG_xA_per90 %>%
               filter(xA_p90 > 0.15 | npxG_p90 > 0.3,
                      Min >= 900),
             color = "red", size = 4) +
  geom_hline(yintercept = 0.3, color = "red", alpha = 0.6) +
  geom_vline(xintercept = 0.15, color = "red", alpha = 0.6) +
  geom_text_repel(
    data = xG_xA_per90 %>%
      filter(xA_p90 > 0.15 | npxG_p90 > 0.3,
             !player %in% c("G. Jesus", "R. Sterling", "S. Agüero",
                            "R. Mahrez", "K. De Bruyne", "S. Mané"),
             Min >= 900),
    aes(label = player, family = "Roboto Condensed", fontface = "bold"),
    seed = 15, size = 3.5,
    min.segment.length = 0, segment.color = "red",
    point.padding = 0.5) +
  geom_mark_hull(
    aes(filter = player %in% c("M. Thuram", 
                               "B. Embolo"), 
        label = "Gladbach's Attacking Trio",
        description = desc_aguero_sterling),
    expand = unit(0.05, "mm"), label.width = unit(60, 'mm'),
    label.buffer = unit(30, "mm"), label.fontsize = c(14, 11),
    label.family = "Roboto Condensed", 
    label.colour = c("green", "black")) +
  geom_mark_circle(
    aes(filter = player == "A. Pléa"),
    expand = unit(3, "mm"), label.width = unit(50, 'mm'),
    label.buffer = unit(30, "mm"), label.fontsize = c(14, 11),
    label.family = "Roboto Condensed", 
    label.colour = c("green", "black"))
```



#### save

```{r}
ggsave(plot = xG_xA_per90_plot, 
       here::here("Premier League 2019-2020/output/xA_xG_per90_1920_MD21.png"),
       height = 10, width = 12)
```

```{r}
plot_logo <- add_logo(
  plot_path = here::here("Premier League 2019-2020/output/xA_xG_per90_1920_MD21.png"),
  logo_path = "https://upload.wikimedia.org/wikipedia/en/f/f2/Premier_League_Logo.svg",
  logo_position = "top right",
  logo_scale = 6)

plot_logo
```

```{r}
image_write(image = plot_logo, 
            here::here("Premier League 2019-2020/output/xA_xG_per90_1920_MD21_logo.png"))
```







